Exploratory Data Analysis

### 2023-11-01 analysis/eda.qmd
poisson

table1 <- data |>
  select(table_one_vars) |>
  tbl_summary(
    by = ich_laterality,
    missing = "no",
    label = list(
      age ~ "Age",
      sex ~ "Sex",
      race ~ "Race",
      ethnicity ~ "Ethnicity",
      time_symptoms_to_ed ~ "LNW to ED Presentation (mins)",
      sbp_baseline ~ "Baseline SBP (mm Hg)",
      nihss_baseline ~ "Baseline NIHSS",
      gcs_baseline ~ "Baseline GCS",
      htn ~ "Hypertension",
      dm2 ~ "Type II Diabetes",
      stroke ~ "Previous Stroke",
      tobacco ~ "Tobacco Use",
      ich_location ~ "ICH Location",
      ich_volume_baseline ~ "ICH Volume (mL)",
      ivh ~ "IVH",
      study ~ "Study"
    )
  ) |>
  add_p() |>
  add_overall() |>
  bold_labels()

@@

table2 <- data |>
  select(table_two_vars) |>
  tbl_summary(
    by = ich_laterality,
    missing = "no",
    label = list(
      neurosurgery_evac ~ "Neurosurgical Intervention",
      evd ~ "Ventriculostomy",
      days_mechanical_ventilation ~ "Intubation Days",
      tracheostomy ~ "Tracheostomy",
      comfort_care_binary ~ "Comfort Care"
    )
  ) |>
  add_p() |>
  add_overall() |>
  bold_labels()

@@

neurosurgery_glm <- glm(
  neurosurgery_evac ~ ich_laterality + age + ich_location + gcs_baseline + ich_volume_baseline + ivh + time_symptoms_to_ed,
  data = data,
  family = binomial
)

model_parameters(neurosurgery_glm,
  centrality = "mean", dispersion = TRUE,
  test = FALSE, verbose = FALSE, ci_method = "hdi", priors = TRUE,
  exponentiate = TRUE
) |>
  print(digits = 2, zap_small = TRUE)

>>>>

table1 <- data_erich_atach |>
  select(table_one_vars) |>
  tbl_summary(
    by = ich_laterality,
    missing = "no",
    label = list(
      age ~ "Age",
      sex ~ "Sex",
      race ~ "Race",
      ethnicity ~ "Ethnicity",
      time_symptoms_to_ed ~ "LNW to ED Presentation (mins)",
      sbp_baseline ~ "Baseline SBP (mm Hg)",
      nihss_baseline ~ "Baseline NIHSS",
      gcs_baseline ~ "Baseline GCS",
      htn ~ "Hypertension",
      dm2 ~ "Type II Diabetes",
      stroke ~ "Previous Stroke",
      tobacco ~ "Tobacco Use",
      ich_location ~ "ICH Location",
      ich_volume_baseline ~ "ICH Volume (mL)",
      ivh ~ "IVH",
      study ~ "Study"
    )
  ) |>
  add_p() |>
  add_overall() |>
  bold_labels()

@@

table2 <- data_erich_atach |>
  select(table_two_vars) |>
  tbl_summary(
    by = ich_laterality,
    missing = "no",
    label = list(
      neurosurgery_evac ~ "Neurosurgical Intervention",
      evd ~ "Ventriculostomy",
      days_mechanical_ventilation ~ "Intubation Days",
      tracheostomy ~ "Tracheostomy",
      comfort_care_binary ~ "Comfort Care"
    )
  ) |>
  add_p() |>
  add_overall() |>
  bold_labels()

@@

neurosurgery_glm <- glm(
  neurosurgery_evac ~ ich_laterality + age + ich_location + gcs_baseline + ich_volume_baseline + ivh + time_symptoms_to_ed,
  data = data_erich_atach,
  family = binomial
)

neurosurgery_glm |>
  tbl_regression(
    exponentiate = TRUE,
    include = ich_laterality
  )

left_right_regression <- function(name, var, family) {
  name <- glm(
    {{ var }} ~ ich_laterality + age + ich_location + gcs_baseline + ich_volume_baseline + ivh + time_symptoms_to_ed,
    data = data_erich_atach,
    family = family
  )

  neurosurgery_glm |>
    tbl_regression(
      exponentiate = TRUE,
      include = ich_laterality
    )
}

left_right_regression(neurosurgery_glm, neurosurgery_evac, binomial)

vent_glm <- glm(
  days_mechanical_ventilation ~ ich_laterality + age + ich_location + gcs_baseline + ich_volume_baseline + ivh + time_symptoms_to_ed,
  data = data_erich_atach,
  family = poisson
)

model_parameters(vent_glm,
  centrality = "mean", dispersion = TRUE,
  test = FALSE, verbose = FALSE, ci_method = "hdi", priors = TRUE,
  exponentiate = TRUE
) |>
  print(digits = 2, zap_small = TRUE)
